---
title: "RWA Assignment - 2"
output: html_notebook
---
Q1
Reading the data
```{r}
the.data <- as.matrix(read.table("ENB_2023.txt"))
```

Setting the seed for replication
```{r}
set.seed(223602808)
```

Taking only certain rows
```{r}
my.data <- the.data[sample(1:671,340),c(1:6)]
```

```{r}
backup_data<-my.data
```


Plotting Scatter Plots 
```{r}
par(mfrow=c(2,3))
```

```{r}
plot(my.data[,6], my.data[,1], main="Scatter plot between Energy use and
     Temperature in kitchen area", xlab="Energy Use (in Wh)", 
     ylab="Temperature (in Celsius)", col=" dark red")
```

```{r}
plot(my.data[,6], my.data[,2], main="Scatter plot between Energy use and
     Humidity in kitchen area", xlab="Energy Use (in Wh)", 
     ylab="Humidity (in Percentage)", col="dark red")
```

```{r}
plot(my.data[,6], my.data[,3], main="Scatter plot between Energy use and
     Temperature outside", xlab="Energy Use (in Wh)", 
     ylab="Temperature (in Celsius)", col="dark red")
```

```{r}
plot(my.data[,6], my.data[,4], main="Scatter plot between Energy use and
     Humidity outisde", xlab="Energy Use (in Wh)", 
     ylab="Humidity (in Percentage)", col="dark red")
```

```{r}
plot(my.data[,6], my.data[,5], main="Scatter plot between Energy use and
     Visibility", xlab="Energy Use (in Wh)", 
     ylab="Visibility (in km)", col="dark red")
```
Importing library
```{r}
library(rcompanion)
```

Plotting Histogram
```{r}
par(mfrow=c(2,3))
```

```{r}
plotNormalHistogram(my.data[,1], main = "Histogram of Temperature in kitchen area", xlab= "Temperature (in Celsius)", breaks=5, las=1, xlim=c(14,26), col="yellow")
```

```{r}
plotNormalHistogram(my.data[,2], main = "Histogram of Humidity in kitchen area", xlab= "Humidity (in Percentage)", breaks=5, las=1, xlim=c(25,55), col="yellow")
```

```{r}
plotNormalHistogram(my.data[,3], main = "Histogram of Temperature outside (from weather station)", xlab= "Temperature (in Celsius)", breaks=5, las=1, xlim=c(0,7),col="yellow")
```

```{r}
plotNormalHistogram(my.data[,4], main = "Histogram of Humidity outside (from weather station)", xlab= "Humidity (in Percentage)", breaks=5, las=1, xlim=c(60,100),col="yellow")
```

```{r}
plotNormalHistogram(my.data[,5], main = "Histogram of Visibility (from weather station)", xlab= "Visibility (in km)", breaks=5, las=1, xlim=c(10,70), col="yellow")
```

```{r}
plotNormalHistogram(my.data[,6], main = "Histogram of Energy use of appliances", xlab= "Energy (in Wh)", breaks=5, las=1,xlim=c(20,200),col="yellow")
```

```{r}
for( i in 1:6) {
  pvalue_variables<-ks.test(jitter(my.data[,i]), "pnorm", mean=mean(my.data[,i]), sd=sd(my.data[,i]))
  print(pvalue_variables)
}
```
KS - Test Result
X1 P-value = 0.4642
X2 P-value = 0.1477
X3 P-value = 0.007026
X4 P-value = 0.06664
X5 P-value = 5.509e-05
Y P-value = 7.383e-14

Since p-value for X1, X2, X4 is > 0.05, there is no significant difference between normal distribution and distribution of variables. Hence leaving the data untransformed.

Also, X3, X5 and Y are not normally distributed as per the KS - test, we need to check for skewness and apply transformation accordingly.

If Skewness is 0, then it means to be a perfect normal distribution
If Skewness is between -0.5 and 0.5, we can approximate it to a normal distribution
If Skewness is > 0.5, it is positively Skewed
If Skewness is <-0.5, it is negatively Skewed

Importing moments library for finding skewness
```{r}
library(moments)
```

Finding skewness for X3
```{r}
print(skewness(my.data[,3]))
```

Finding skewness for X5
```{r}
print(skewness(my.data[,5]))
```

Finding skewness for Y
```{r}
print(skewness(my.data[,6]))
```
Skewness:
X3 = 0.01446961
X5 = 0.7299919
Y = 1.917926

Since Skewness X3 is very close 0, we can ignore performing any transformation to it.

Since X5 and Y is > 0.5, they are positively Skewed. Hence we will apply log transformation on X5 and Y.

```{r}
pearson_results<-array(0,5)
```

```{r}
for(i in 1:5){
  pearson_results[i]<-cor(my.data[,6], my.data[,i])
}
```

```{r}
pearson_results
```

```{r}
spearman_results<-array(0,5)
```

```{r}
for(i in 1:5){
  spearman_results[i]<-cor(my.data[,6], my.data[,i])
}
```

```{r}
spearman_results
```

We are choosing X1, X2, X3 and X5 based on Pearson correlation and coefficient and Spearman's rank correlation coefficient.
We did not select X4 because it has the weakest relationship with Y.

Applying log transformation on X5 and Y
Creating the log function
```{r}
log.fun<-function(x){
  result=log10(x)
  return(result)
}
```

Applying log on X5
```{r}
my.data[,5] <- log.fun(my.data[,5])
```

```{r}
log.transform.5 <- my.data[,5]
```

```{r}
log.transform.5
```
Applying log on Y
```{r}
my.data[,6] <- log.fun(my.data[,6])
```

```{r}
log.transform.Y <- my.data[,6]
```

```{r}
log.transform.Y
```
Applying min-max
```{r}
minmax<-function(x){
  result=(x-min(x))/(max(x)-min(x))
  return(result)
}
```

```{r}
my.data[,1] <- minmax(my.data[,1])
```

```{r}
my.data[,2] <- minmax(my.data[,2])
```

```{r}
my.data[,2]
```

```{r}
my.data[,3] <- minmax(my.data[,3])
```

```{r}
my.data[,4] <- minmax(my.data[,4])
```

```{r}
my.data[,5] <- minmax(my.data[,5])
```

```{r}
my.data[,6] <- minmax(my.data[,6])
```

```{r}
par(mfrow=c(2,3))
```

```{r}
plotNormalHistogram(my.data[,1], main = "Histogram of Humidity in kitchen area after Min-Max transformation", xlab= "Humidity (in Percentage)", las=1,col="green")
```

```{r}
plotNormalHistogram(my.data[,2], main = "Histogram of Humidity in kitchen area after Min-Max transformation", xlab= "Humidity (in Percentage)", las=1,col="green")
```
```{r}
plotNormalHistogram(my.data[,3], main = "Histogram of Humidity in kitchen area after Min-Max transformation", xlab= "Humidity (in Percentage)", las=1,col="green")
```

```{r}
plotNormalHistogram(my.data[,5], main = "Histogram of Humidity in kitchen area after Min-Max transformation", xlab= "Humidity (in Percentage)", las=1,col="green")
```

```{r}
plotNormalHistogram(my.data[,6], main = "Histogram of Humidity in kitchen area after Min-Max transformation", xlab= "Humidity (in Percentage)", las=1,col="green")
```

Since we do not need X4 we can remove that feature 
```{r}
my.data<-my.data[,-4]
```

Verifying the data
```{r}
View(my.data)
```

Writing the data to another file
```{r}
write.table(my.data, "likith_transformed_sample.txt")
```

Importing AggWaFit.R
```{r}
source("AggWaFit718.R")
```

Reading the data and converting it to a matrix for manipulation
```{r}
transformed.data<-as.matrix(read.table("likith_transformed_sample.txt"))
```

```{r}
View(transformed.data)
```

Building Models
weights for Weighted Arithmetic Mean with fit.QAM()
```{r}
fit.QAM(transformed.data,"out_AM.txt","stat_AM.txt",g=AM,g.inv=invAM)
```
RMSE 0.167044631433746
Av. abs error 0.128133480607362
Pearson correlation 0.589251762910605
Spearman correlation 0.543675440205338

weights for Power Mean p=0.5 with fit.QAM()
```{r}
fit.QAM(transformed.data,"out_PM05.txt","stat_PM05.txt",g=PM05,g.inv=invPM05)
```
RMSE 0.172205586055085
Av. abs error 0.131275041599399
Pearson correlation 0.56413850037432
Spearman correlation 0.529207819083485

weights for Power Mean p=2 with fit.QAM()
```{r}
fit.QAM(transformed.data,"out_QM.txt","stat_QM.txt",g=QM,g.inv=invQM)
```
RMSE 0.162658294298987
Av. abs error 0.125277679913978
Pearson correlation 0.607491775262898
Spearman correlation 0.558280759785093

weights for Ordered Weighted Average with fit.OWA()
```{r}
fit.OWA(transformed.data,"out_OWA.txt","stat_OWA.txt")
```
RMSE 0.178060803916844
Av. abs error 0.139440884735571
Pearson correlation 0.473244183224705
Spearman correlation 0.423779691018706
Orness 0.570405825156529

weights for Choquet Integral with fit.choquet()
```{r}
fit.choquet(transformed.data,"out_choq.txt","stat_choq.txt")
```
RMSE 0.156912634794026
Av. abs error 0.121800581867797
Pearson Correlation 0.631595637242979
Spearman Correlation 0.582679534069074
Orness 0.643574950868064

Using model for prediction
Since we can see that the choquet provides the lowest RMSE and Av. abs error, we can select choquet model for prediction
X1=22; X2=38; X3=4; X4=88.2; X5=34

Selecting only X1, X2, X3 and X5 because we trained the model with these features
```{r}
new.data <- c(22,38,4,34)
```

```{r}
transform.new.data<-new.data
```

Transforming the new data
Since we did not apply any transformation for X1, X2 and X3 features, we are also not going to apply any transformation for the new data
min-maxing X1
```{r}
transform.new.data[1]<-(new.data[1]-min(backup_data[,1]))/(max(backup_data[,1])-min(backup_data[,1]))
```

min-maxing X2
```{r}
transform.new.data[2]<-(new.data[2]-min(backup_data[,2]))/(max(backup_data[,2])-min(backup_data[,2]))
```

min-maxing X3
```{r}
transform.new.data[3]<-(new.data[3]-min(backup_data[,3]))/(max(backup_data[,3])-min(backup_data[,3]))
```

Applying log, since we applied log transformation for X5
```{r}
transform.new.data[4]<-log.fun(new.data[4])
```

min-maxing X5
```{r}
transform.new.data[4]<-(transform.new.data[4]-min(log.transform.5))/(max(log.transform.5)-min(log.transform.5))
```

```{r}
transform.new.data
```

Taking the choquet weights from the stat_choq output file
```{r}
ChoqWeights <- c(0.54193303432683, 0, 0.54193303432683, 0.773863518370135, 0.999999999997865, 0.773863518370135, 0.999999999997865, 0.402146540858998, 0.541933034326625, 0.402146540858998, 0.541933034326625, 0.773863518370138, 0.999999999999115, 0.773863518370138, 0.999999999999115)
```

Prediction MAIN EVENT WRESTLEMANIA...!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
```{r}
result <- choquet(transform.new.data, ChoqWeights)
```

```{r}
result
```

Reversing the transformation
```{r}
transform.result<-result*(max(log.transform.Y)-min(log.transform.Y))+min(log.transform.Y)
```

```{r}
transform.result
```

```{r}
predicted_output<-10^(transform.result)
```

```{r}
predicted_output
```


